Classification of Swedish Forest Sector Innovation

### 2023-03-23 docs/paper.qmd
add to analysis and abstract

### By Sector

#### Bioeconomy Vision

bv_sectors = pd.read_sql(
    """
SELECT
  c.Category as vision,
  sni_codes.label as sector,
  count(bv.bioeconomy_vision) as count
FROM
  bioeconomy_visions as bv
  join use_sectors ON bv.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] as c ON bv.bioeconomy_vision = c.Code
WHERE 
  NOT EXISTS(
   SELECT
      *
    FROM
      bioeconomy_visions AS bv2
    WHERE
      bv2.sinno_id = bv.sinno_id
      AND bv2.bioeconomy_vision = 0
)
GROUP BY
  sector,
  bioeconomy_vision;
""",
    conn,
)

bv_matrix = prepare_heatmap_data(
    bv_sectors, index_col="sector", cols_col="vision", values_col="count"
)

plot_heatmap(bv_matrix, "Count Bioeconomy Vision by Sector Excluding Uncertains")
```

#### Eco-Innovations

```{python}
ei_sectors = pd.read_sql(
    """
SELECT
  c.Category as innovation_type,
  sni_codes.label as sector,
  count(ei.innovation_type) as count
FROM
  eco_innovations as ei
  join use_sectors ON ei.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] as c ON ei.innovation_type = c.Code
WHERE 
  NOT EXISTS(
   SELECT
      *
    FROM
      eco_innovations AS ei2
    WHERE
      ei2.sinno_id = ei.sinno_id
      AND ei2.innovation_type = "000"
)
GROUP BY
  sector,
  innovation_type;
""",
    conn,
)

```
### Over Time

#### Bioeconomy Visions Using SWINNO

#### Bioeconomy Visions Using Articles

@@

At most we record

@@

@@

```{python}
bvu_sectors = pd.read_sql(
    """
SELECT
  c.Category AS vision,
  sni_codes.label AS sector,
  count(bv.bioeconomy_vision) AS count
FROM
  bioeconomy_visions AS bv
  join use_sectors ON bv.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] AS c ON bv.bioeconomy_vision = c.Code
GROUP BY
  sector,
  bioeconomy_vision;
""",
    conn,
)

@@

#### Eco-Innovations Over Time

##### SWINNO

##### Articles
```{python}

#| fig-caption: Count of Eco-Innovations by Year.

eia_years = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  count(ei.innovation_type) AS innovation_count,
  innovation.[Year of commercialization] AS Year,
  SUBSTR(ei.innovation_type, 1,1) as top_cat
FROM
  eco_innovations_articles AS ei
  JOIN innovation ON ei.sinno_id = innovation.[SINNO ID]
  JOIN [classification-codes] AS codes ON ei.innovation_type = codes.Code
WHERE
  TRIM(innovation.[Year of commercialization]) IS NOT ""
GROUP BY
  Year,
  ei.innovation_type;
""",
    conn,
)

eiac_years = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  count(ei.innovation_type) AS innovation_count,
  innovation.[Year of commercialization] AS year,
  SUBSTR(ei.innovation_type, 1,1)
FROM
  eco_innovations_articles AS ei
  JOIN innovation ON ei.sinno_id = innovation.[SINNO ID]
  JOIN [classification-codes] AS codes ON ei.innovation_type = codes.Code
WHERE
  NOT EXISTS (
    SELECT
      *
    FROM
      eco_innovations_articles AS ei2
    WHERE
      ei2.sinno_id = ei.sinno_id
      AND ei2.innovation_type = "000"
  )
  AND TRIM(innovation.[Year of commercialization]) IS NOT ""
GROUP BY
  year,
  ei.innovation_type;
""",
    conn,
)

plot_counts(
    eia_years,
    eiac_years,
    category_col="Type",
    y="innovation_count",
    legend_cols = 8,
    y_label="Count of Type",
    show_legend=False
)

>>>>

## Bioeconomy Vision

Examining the split of bioeconomy visions across sectors in @fig-bva-sectors, reveals a strong concentration of bioresource related innovations in the forestry sector.

```{python}
#| label: fig-bva-sectors
#| fig-cap: Heatmap of Bioeconomy Visions by Sector

bva_sectors = pd.read_sql(
    """
SELECT
  c.Category as vision,
  sni_codes.label as sector,
  count(bva.bioeconomy_vision) as count
FROM
  bioeconomy_visions_articles as bva
  join use_sectors ON bva.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] as c ON bva.bioeconomy_vision = c.Code
WHERE 
  NOT EXISTS(
   SELECT
      *
    FROM
      bioeconomy_visions_articles AS bva2
    WHERE
      bva2.sinno_id = bva.sinno_id
      AND bva2.bioeconomy_vision = 0
)
GROUP BY
  sector,
  bioeconomy_vision;
""",
    conn,
)

bva_matrix = prepare_heatmap_data(
    bva_sectors, index_col="sector", cols_col="vision", values_col="count"
)

plot_heatmap(bva_matrix, "Count Bioeconomy Vision by Sector Excluding Uncertains")
```

@fig-bva-years suggests no clear pattern in the absolute count of visions assigned to innovations.
Partially this might stem from a small number of innovations labeled so far, however, no clearer pattern emerges in the larger dataset using only SWINNO either (@fig-bv-years).
The small number of biotechnology related visions is due to the chemistry sector not yet being included in the labelling.

```{python}
#| label: fig-bva-years
#| fig-cap: Count of Bioeconomy Visions by Year

@@

## Eco-Innovations

Looking at the eco-innovation types by sector reveals that the biggest category and most heavily used in the forest and timber sector are innovations aimed to prolong the lifecylce of products used therin (@fig-ei-sectors)
```{python}
#| label: fig-eia-sectors
#| fig-cap: Heatmap of Eco-Innovations by Sector

eia_sectors = pd.read_sql(
    """
SELECT
  c.Category as innovation_type,
  sni_codes.label as sector,
  count(eia.innovation_type) as count
FROM
  eco_innovations_articles as eia
  join use_sectors ON eia.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] as c ON eia.innovation_type = c.Code
WHERE 
  NOT EXISTS(
   SELECT
      *
    FROM
      eco_innovations_articles AS eia2
    WHERE
      eia2.sinno_id = eia.sinno_id
      AND eia2.innovation_type = "000"
)
GROUP BY
  sector,
  innovation_type;
""",
    conn,
)

eia_sectors_matrix = prepare_heatmap_data(
    eia_sectors, index_col="sector", cols_col="innovation_type", values_col="count"
)

plot_heatmap(eia_sectors_matrix, title="Eco-Innovation Type by Sector")

For the count of eco-innovation types by year, the legend had to be surpressed, as the amount of categories made the plots unreadable.
Just as for bioeconomy visions @fig-eia-year shows no clear pattern yet.
@fig-ei-year-swinno does little to improve this.
The biggest categories in that dataset are "Not Eco-Innovation" (dark blue), and "Automatization" (dark pink).
Visualizing these data is challenging and suggestions warmly welcome.

```{python}
#| label: fig-eia-year
#| fig-cap: Count of Eco-Innovations by Year

eia_years = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  count(eia.innovation_type) AS innovation_count,
  innovation.[Year of commercialization] AS Year,
  SUBSTR(eia.innovation_type, 1,1) as top_cat
FROM
  eco_innovations_articles AS eia
  JOIN innovation ON eia.sinno_id = innovation.[SINNO ID]
  JOIN [classification-codes] AS codes ON eia.innovation_type = codes.Code
WHERE
  TRIM(innovation.[Year of commercialization]) IS NOT ""
GROUP BY
  Year,
  eia.innovation_type;
""",
    conn,
)

eiac_years = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  count(eia.innovation_type) AS innovation_count,
  innovation.[Year of commercialization] AS year,
  SUBSTR(eia.innovation_type, 1,1)
FROM
  eco_innovations_articles AS eia
  JOIN innovation ON eia.sinno_id = innovation.[SINNO ID]
  JOIN [classification-codes] AS codes ON eia.innovation_type = codes.Code
WHERE
  NOT EXISTS (
    SELECT
      *
    FROM
      eco_innovations_articles AS eia2
    WHERE
      eia2.sinno_id = eia.sinno_id
      AND eia2.innovation_type = "000"
  )
  AND TRIM(innovation.[Year of commercialization]) IS NOT ""
GROUP BY
  year,
  eia.innovation_type;
""",
    conn,
)

plot_counts(
    eia_years,
    eiac_years,
    category_col="Type",
    y="innovation_count",
    legend_cols = 8,
    y_label="Count of Type",
    show_legend=False
)
```

So far, there is not much to make of these figures.
The subset of innovations in SWINNO analyzed is too small to descern any real trends.
However, there is probable cause to believe that the tendency of dominating bioresource vision related innovations will persist.
It is unsurprising that in the core forestry sector (logging, timber) these type of innovations are more frequent than e.g., biotechnology related visions.
Perhpas surprising is that, despite the small number of innovation labelled so far and the methodological disadvantage of LBIO towards bioecology innovations, three were possibly already identified.
There occurance in the 1980s might suggest taht they were the outcome of a temporary increased awareness of environmental issues in the forestry sector at that time.

@@

### SWINNO

@@

```{python}
#| label: fig-bv-sectors
#| fig-cap: Heatmap of Bioeconomy Visions by Sector (SWINNO)

bvu_sectors = pd.read_sql(
    """
SELECT
  c.Category AS vision,
  sni_codes.label AS sector,
  count(bv.bioeconomy_vision) AS count
FROM
  bioeconomy_visions AS bv
  join use_sectors ON bv.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] AS c ON bv.bioeconomy_vision = c.Code
GROUP BY
  sector,
  bioeconomy_vision;
""",
    conn,
)

@@

#### Bioeconomy Visions Over Time

```{python}
#| label: fig-bv-years
#| fig-cap: Count of Bioeconomy Visions by Year (SWINNO)

#### Eco-Innovations by Sector

```{python}
#| label: fig-ei-sectors
#| fig-cap: Heatmap of Eco-Innovations by Sector (SWINNO)

ei_sectors = pd.read_sql(
    """
SELECT
  c.Category as innovation_type,
  sni_codes.label as sector,
  count(ei.innovation_type) as count
FROM
  eco_innovations as ei
  join use_sectors ON ei.sinno_id = use_sectors.[SINNO ID]
  join sni_codes ON SUBSTR(use_sectors.use_sectors, 1, 2) = sni_codes.code
  join [classification-codes] as c ON ei.innovation_type = c.Code
WHERE 
  NOT EXISTS(
   SELECT
      *
    FROM
      eco_innovations AS ei2
    WHERE
      ei2.sinno_id = ei.sinno_id
      AND ei2.innovation_type = "000"
)
GROUP BY
  sector,
  innovation_type;
""",
    conn,
)

#### Eco-Innovations Over Time
```{python}
#| label: fig-ei-year-swinno
#| fig-cap: Count of Eco-Innovations by Year (SWINNO).

ei_years = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  count(ei.innovation_type) AS innovation_count,
  innovation.[Year of commercialization] AS Year,
  SUBSTR(ei.innovation_type, 1,1) as top_cat
FROM
  eco_innovations AS ei
  JOIN innovation ON ei.sinno_id = innovation.[SINNO ID]
  JOIN [classification-codes] AS codes ON ei.innovation_type = codes.Code
WHERE
  TRIM(innovation.[Year of commercialization]) IS NOT ""
GROUP BY
  Year,
  ei.innovation_type;
""",
    conn,
)

eic_years = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  count(ei.innovation_type) AS innovation_count,
  innovation.[Year of commercialization] AS year,
  SUBSTR(ei.innovation_type, 1,1)
FROM
  eco_innovations AS ei
  JOIN innovation ON ei.sinno_id = innovation.[SINNO ID]
  JOIN [classification-codes] AS codes ON ei.innovation_type = codes.Code
WHERE
  NOT EXISTS (
    SELECT
      *
    FROM
      eco_innovations AS ei2
    WHERE
      ei2.sinno_id = ei.sinno_id
      AND ei2.innovation_type = "000"
  )
  AND TRIM(innovation.[Year of commercialization]) IS NOT ""
GROUP BY
  year,
  ei.innovation_type;
""",
    conn,
)

ei_years = ei_years.set_index("Year")
eic_years = eic_years.set_index("year")

plot_counts(
    ei_years,
    eic_years,
    category_col="Type",
    y="innovation_count",
    legend_cols = 8,
    y_label="Count of Type",
    show_legend=False
)
